---
title: "Crossword puzzle"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(scales)

theme_set(theme_light())
```

## R Markdown

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

## Load weekly data

```{r load_data, echo=FALSE}
big_dave <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-04-19/big_dave.csv')
times <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-04-19/times.csv')
```

```{r, echo=FALSE}
clues <- times %>%
  bind_rows(big_dave) %>%
  select(-rowid) %>%
  extract(clue, c("clue", "lengths"), "(.*) \\((.*)\\)") %>%
  mutate(definition_length = str_length(definition)) %>%
  mutate(year = year(puzzle_date),
         definition_index = str_locate(clue, fixed(definition))[, 1],
         definition_pos = (definition_index - 1) / (str_length(clue) - str_length(definition)))

clues
```


### Initial processing

First let's see the puzzles by month

```{r processing, echo=FALSE}
clues %>%
  count(puzzle_date = floor_date(puzzle_date, "month"), source) %>%
  ggplot(aes(puzzle_date, n, fill = source)) +
  geom_col()
```

and then quarter
```{r, echo=FALSE}
clues %>%
  count(puzzle_date = floor_date(puzzle_date, "quarter"), source) %>%
  ggplot(aes(puzzle_date, n, fill = source)) +
  geom_col()
```
What is the distribution of the definitions in the clues?
```{r}
clues %>%
  ggplot(aes(definition_pos)) +
  geom_histogram(boundary = 0, binwidth = 0.05)
```
This histogram tells us that a trick to solving cryptograms puzzles is that the definition is most likely at the beginning or the end of the clue.

```{r}
clues %>%
  group_by(year, source) %>%
  summarize(pct_missing = mean(is.na(definition_pos))) %>%
  ggplot(aes(year, pct_missing, color = source)) + 
  geom_line()
```

```{r}
clues %>%
  filter(!is.na(definition_pos)) %>%
  group_by(year, source) %>%
  summarize(pct_start_or_end = mean(definition_pos %in% c(0, 1)),
            n = n()) %>%
  filter(n >= 1000) %>%
  ggplot(aes(year, pct_start_or_end, color = source)) + 
  geom_line()
```
It looks like Big Dave is more likely to have the definition be located at the start or the end of the clue.

```{r}
clues %>%
  filter(!is.na(definition_pos),
         source == "bigdave44") %>%
  mutate(start_end = definition_pos %in% c(0, 1)) %>%
  glm(start_end ~ year, data = ., family = "binomial") %>%
  summary()
```

```{r}
clues %>%
  ggplot(aes(definition_length, fill = source)) + 
  geom_histogram() + 
  facet_wrap(~ source, ncol = 1)
```

```{r}
clues %>%
  ggplot(aes(definition_length, str_length(answer))) + 
  geom_point()
```

```{r}
clues %>%
  filter(!is.na(definition_pos)) %>%
  count(definition_length, answer_length = str_length(answer)) %>%
  ggplot(aes(definition_length, answer_length, fill = n)) + 
  geom_tile()

clues %>%
  filter(!is.na(definition_pos),
         !is.na(answer)) %>%
  summarize(cor = cor(definition_length, str_length(answer)))
```
```{r}
clues %>%
  filter(!is.na(definition_pos),
         !is.na(answer)) %>%
  with(cor.test(definition_length, str_length(answer)))
```





